\begin{enumerate}[label=\arabic*.,ref=\theenumi]
%\begin{enumerate}[label=\thesubsection.\arabic*.,ref=\thesubsection.\theenumi]
%
\item Make the pin connections in Table \ref{table:stm_ssd} using Figs. \ref{fig:sevenseg} and \ref{fig:stm_blue}.
	
%
\begin{table}[!htb]
\begin{center}
\input{stm32/sevenseg/figs/stm_ssd}
\end{center}
\caption{STM-32 and Seven Segment Display Connections}
\label{table:stm_ssd}
\end{table}
%
\item Execute the following code 
\begin{lstlisting}
stm32/sevenseg/codes/sevenseg_example.c
\end{lstlisting}

%\begin{problem}
%In the STM32F103C8T6 directory,
%\begin{lstlisting}
%cp sevenseg.c main.c
%\end{lstlisting}
%Generate the number 0 by executing \textbf{main.c} and flashing to the STM32. 
%\end{problem}	
%
\item Explain the process of generating the number 0 using the following instruction.
\begin{lstlisting}
GPIOB->ODR = 0xFC08;
\end{lstlisting}
\solution ODR is the Output Data Register, which is used to write outputs to the GPIO pins. The 16 bit number 0xFC08 on the RHS represents the pin configuration for the pins of port B of STM32F103C8T6, which are numbered PB15-PB0 in that order.  See Table \ref{table:stm_ssd}.
\item Repeat the above exercise to generate the numbers 1-9 on the display.
\item The previous instructions set the bits in the unused ports PB15-PB10 and PB2-PB0. This may be undesirable in some cases. Generate 0 by not disturbing 
the unused pins.
\\
\solution The following instructions help accomplish this. The first instruction resets PB4-PB9.  The second instruction sets the PB3 pin. The other pins are
undisturbed.
\begin{lstlisting}
GPIOB->BRR = (1<<4)|(1<<5)|(1<<6)|(1<<7)|(1<<8)|(1<<9); // (Led ON)		
GPIOB->BSRR = (1<<3); // (Led OFF)					
\end{lstlisting}
%\section{Manual Display Control}
%\input{./chapters/chapter1}
%
\item Write a program to take a 4-bit BCD as input from hardware (GND or VDD) and show the next number on the seven segment display.
\\
\solution The following program takes 4 bits as input from pins PB12-PB15 and displays the output on a seven segment display. The next number
can be displayed by slightly modifying the code.
\begin{lstlisting}
stm32/sevenseg/codes/bin2dec_example.c
\end{lstlisting}
\end{enumerate}

