\section{UART Communication between Vaman-ESP32 and Arduino}
This section describes how to communicate between Vaman-ESP32 and Arduino UNO 
through UART Protocol. The Unknown resistance is measured using Arduino and 
sending the value to Vaman through UART and displaying the unknown resistance on
ESP32 Webserver.
\subsection{Components}
The components required are listed in \autoref{table:uart-components}.
\begin{table}[!ht]
\centering
\input{vaman-esp32/uart/figs/components.tex}
\caption{Components}
\label{table:uart-components}
\end{table}

\subsection{Connections}
\begin{enumerate}
\item
Connect the Vaman and Arduino as shown in \autoref{Tab:uart-Connections}.

\begin{table}[!ht]
\centering
\input{vaman-esp32/uart/figs/connections.tex}
\caption{Connections}
\label{Tab:uart-Connections}
\end{table}
\item
The Vaman pin diagram is available in \autoref{fig:vaman-pin_sheet}.

\item Upload the following code to Arduino UNO

\begin{lstlisting}
vaman-esp32/uart/codes/UNO
\end{lstlisting}
\end{enumerate}
\subsection{Measuring the resistance}
\begin{enumerate}
\item
Connect the 5V pin of the Vaman-ESP32 to an extreme pin of the breadboard shown
in \autoref{fig:breadboard}. Let this pin be $V_{cc}$.
\item
Connect the GND pin of the Vaman-ESP32 to the opposite extreme pin of the 
breadboard.
\item
Let $R_1$ be the known resistor and $R_2$ be the unknown resistor. Connect $R_1$
and $R_2$ in series such that $R_1$ is connected to $V_{cc}$ and $R_2$ is
connected to GND. Refer to \autoref{fig:voltage_divider}.
\item
Connect the junction between the two resistors to the A0 pin on the Arduino
board.
\item
Now power the Vaman board.
\item
Execute the following code after editing the WiFi credentials
\begin{lstlisting}
vaman-esp32/uart/codes/VAMAN
\end{lstlisting}
\end{enumerate}
\subsection{Displaying the Measured resistance on website}
\begin{enumerate}
\item The unknown resistance is measured and diplayed the measured resistance on
the Vaman-ESP32 webserver.
\item After flashing the code to Vaman-ESP32, the board will be connected to the
WiFi credentials provided.
\item Now connect the same WiFi credentials to the mobile phone for accessing
the IP address, which can be accessed by 
\begin{lstlisting}
ifconfig
nmap -sn 192.168.x.x/24
\end{lstlisting}
\item Change the IP address in the second command accordingly with the IP
address provided by first command.
\item By the above commands the IP address of Vaman-ESP32 will be diplayed.
\item Now the Vaman-ESP32 will be hosting a webserver.
\item In order to access the webserver type the IP address of the Vaman-ESP32 in
the web browser.
\item In the website loaded by the IP address of Vaman-ESP32 the unknown 
resistance is displayed as shown in \autoref{fig:website}.
\end{enumerate}
